**Density Dependence**

### 2023-02-15 Rmd/report mac.Rmd
report.R and Rmd

library(captioner)     # captions
tab_nums <- captioner::captioner(prefix = "Table", levels=2, type=c("n","n"), infix=".")
fig_nums <- captioner::captioner(prefix = "Figure", levels=2, type=c("n","n"), infix=".")

@@

# Executive summary

@@

tab_nums(name    = "section1_tab", level = 1, display = FALSE)
fig_nums(name    = "section1_fig", level = 1, display = FALSE)

@@

@@

fig_nums(
  name    = "cond_mat", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Maturity at age by year and cohort"))

@@

fig_nums(
  name    = "cond_natmor", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Natural mortality at age by year and cohort (all ages and years the same M)"))

@@

fig_nums(
  name    = "cond_ddwaa", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Density dependence and weight at age."))

@@

fig_nums(
  name    = "cond_gammwaa", level = 2, display = FALSE,
  caption = paste0(mystkname, ". GAMM analysis of density dependence and weight at age."))

@@

tab_nums(
  name    = "cond_gammcoefficients", level = 2, display = FALSE,
  caption = paste0(mystkname, ". GAMM coefficients of density dependence and weight at age."))

@@

fig_nums(
  name    = "cond_lmwaa", level = 2, display = FALSE,
  caption = paste0(mystkname, ". LM analysis of density dependence and weight at age."))

@@

tab_nums(
  name    = "cond_lmsummary", level = 2, display = FALSE,
  caption = paste0(mystkname, ". LM summary of density dependence and weight at age."))

@@

fig_nums(
  name    = "cond_ddmat", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Analysis of density dependence and maturity at age."))

@@

fig_nums(
  name    = "cond_matogive", level = 2, display = FALSE,
  caption = paste0(mystkname, ". Estimated maturity ogive at weight"))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_mass.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_maturity.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_sim_dd_m.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_eq_yield.jpg")))

@@

# knitr::include_graphics(path=file.path(resultsdir, paste0(mystk,"_om.jpg")))

@@

@@

Forward projections with F=fmsy (fwd), 0.8xfmsy?, 1.0xfmsy, 1.2xfmsy?

@@

>>>>

library(captioner)     # captions
tab_nums <- captioner::captioner(prefix = "Table", levels=1, type=c("n"), infix=".")
fig_nums <- captioner::captioner(prefix = "Figure", levels=1, type=c("n"), infix=".")

@@

**Executive summary**

@@

# captioner::bump(fig_nums, level=1)
# fig_nums(name    = "section1_fig", caption = "section1_fig", level = 1, display = FALSE)
# tab_nums(name    = "section1_tab", caption = "section1_tab", level = 1, display = FALSE)

@@

# fig_nums(name    = "section2_fig", caption = "section2_fig", level = 1, display = FALSE)
# tab_nums(name    = "section2_tab", caption = "section2_tab", level = 1, display = FALSE)

@@

fig_nums(
  name    = "cond_mat", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Maturity at age by year and cohort"))

@@

fig_nums(
  name    = "cond_natmor", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Natural mortality at age by year and cohort (all ages and years the same M)"))

@@

fig_nums(
  name    = "cond_ddwaa", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Density dependence and weight at age."))

@@

fig_nums(
  name    = "cond_gammwaa", level = 1, display = FALSE,
  caption = paste0(mystkname, ". GAMM analysis of density dependence and weight at age."))

@@

tab_nums(
  name    = "cond_gammcoefficients", level = 1, display = FALSE,
  caption = paste0(mystkname, ". GAMM coefficients of density dependence and weight at age."))

@@

fig_nums(
  name    = "cond_lmwaa", level = 1, display = FALSE,
  caption = paste0(mystkname, ". LM analysis of density dependence and weight at age."))

@@

tab_nums(
  name    = "cond_lmsummary", level = 1, display = FALSE,
  caption = paste0(mystkname, ". LM summary of density dependence and weight at age."))

@@

fig_nums(
  name    = "cond_ddmat", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Analysis of density dependence and maturity at age."))

@@

fig_nums(
  name    = "cond_matogive", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Estimated maturity ogive at weight"))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_sim_dd_mass.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_sim_dd_maturity.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_sim_dd_m.jpg")))

@@

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_eq_yield.jpg")))

@@

[to be done]

**Density dependence in mass-at-age**

fig_nums(
  name    = "om_VPADDM", level = 1, display = FALSE,
  caption = "Simulation of density dependence in Mass-at-age")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_VPADDM_4panels.jpg")))

@@

_`r fig_nums("om_VPADDM")`_

@@

**Density dependence in mass-at-age and maturity at age**

fig_nums(
  name    = "om_VPADDMM", level = 1, display = FALSE,
  caption = "Simulation of density dependence in Mass-at-age and Maturity at age")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_VPADDMM_4panels.jpg")))

@@

_`r fig_nums("om_VPADDMM")`_

**Density dependence in mass-at-age, maturity at age and M at age**

fig_nums(
  name    = "om_VPADDMMM", level = 1, display = FALSE,
  caption = "Simulation of density dependence in Mass-at-age, maturity at age and M at age")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_VPADDMMM_4panels.jpg")))

_`r fig_nums("om_VPADDMMM")`_

**Comparison of equilibrium curves for density dependence analyses: biomass against yield**

fig_nums(
  name    = "om_eqyield", level = 1, display = FALSE,
  caption = "Equilibrium curves for density dependence analyses: biomass against yield")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_om_biomass_yield.jpg")))

_`r fig_nums("om_eqyield")`_

**Comparison of equilibrium curves for density dependence analyses: biomass against F**

fig_nums(
  name    = "om_eqf", level = 1, display = FALSE,
  caption = "Equilibrium curves for density dependence analyses: biomass against F")

knitr::include_graphics(path=file.path(figuresdir, paste0(mystk,"_om_biomass_F.jpg")))

_`r fig_nums("om_eqf")`_
